---
title: "Interesting R Examples"
author: "Duygu Can - BDA 503 - Fall 2017"
---
```{r,echo=FALSE,results="hide"}
library(knitr)
opts_chunk$set(tidy.opts=list(width.cutoff=60),tidy=TRUE)
```

```{r,echo=FALSE,eval=FALSE}
rmarkdown::render("/Users/berkorbay/Dropbox/Courses_given/MEF_BDA_503_2017F/Guidelines/example_homework_1.Rmd",output_format="pdf_document")
rmarkdown::render("/Users/berkorbay/Dropbox/Courses_given/MEF_BDA_503_2017F/Guidelines/example_homework_1.Rmd",output_format="html_document")
```

1. [An Introduction to Stock Market Data Analysis with R (Part 1)](https://ntguardian.wordpress.com/2017/03/27/introduction-stock-market-data-r-1/)

    This example is importan because it shows basic tools for handling and analyzing stock market data with R. The stock data is obtained from [Yahoo! Finance](https://finance.yahoo.com/). Later four prices  for each date (open, high, low, and close) is visualized by **Japanese candlestick plot**. Two transformations are caried out on the raw data: 
    + Stock's Return
    + Change of each stock per day
    
    Then, the author employs *moving averages* to smooth the series and to identify its trends. It is a nice example to play with time series data but I still think that financial data is boring.

2.
